Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/non_greedy_choice.tex
fixup the finding
tweak

\begin{finding}\label{find:non_greedy_choice}
\textit{Under the non-greedy choice model, \TS is weakly dominant as long as $T$ is sufficiently large}
\end{finding}

@@

However, it takes a significant amount of randomness and a relatively large time horizon for this convergence to occur. Even with $T = 10000$ and $\epsilon = 0.1$ we see that \DEG still outperforms \DG on the Heavy-Tail MAB instance as well as that \TS only starts to become weakly dominant at $T = 10000$ for the Uniform MAB instance. Additionally Table \ref{tab:non_greedy_table} also shows that another difference between the two choice models is that HardMaxWithRandom leads to lower variance in market shares across simulations compared to HardMax.

>>>>

\begin{finding}\label{find:non_greedy_choice}
\textit{Under the HardMaxWithRandom choice model \TS is weakly dominant as long as $T$ is sufficiently large. However, both $T$ and $\epsilon$ have to be relatively large for this to occur.}
\end{finding}

@@

However, it takes a significant amount of randomness and a relatively large time horizon for this convergence to occur. Even with $T = 10000$ and $\epsilon = 0.1$ we see that \DEG still outperforms \DG on the Heavy-Tail MAB instance as well as that \TS only starts to become weakly dominant at $T = 10000$ for the Uniform MAB instance. Table \ref{tab:non_greedy_table} also shows that another difference between the two choice models is that HardMaxWithRandom leads to lower variance in market shares across simulations compared to HardMax.
